Rising from the Ashes II.: something something

### 2024-09-02 paper/ms.tex
Add more about how SoI was selected

@@

The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models. Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy is hardly cause to firmly assert that the fiducial evolution is incorrect.} is not straightforward nor, in our opinion, even possible. However, we do offer one reasonable explanation -- the SFE at the high densities more present at high-$z$ is too low.

>>>>

We examined the abundance distribution of this sample of subhalos by eye. Not many subhalos had multimodal structure, and any structure that was present was relatively weak compared to that observed in the Milky Way. We then applied a post-processing to the \MgFe{} of stars by adding to each star particle a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time of each star particle. With this post-processing, we found that much more structure was generally present and we selected subhalo 172175 (at snapshot 40) for its particular resemblance to the Milky Way. We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99). We refer to this subhalo as our subhalo of interest (SoI).

@@

The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models. Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} is not straightforward nor, in our opinion, even possible. However, we do offer one reasonable explanation -- the SFE at the high densities more present at high-$z$ is too low.
